Between-dataset comparisons

### 2019-11-18 analysis/reports/cross_dataset.Rmd
add .05 line

skew_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_skew_high, color = singletons, size = as.factor(nsites))) +
  geom_point() +
  theme_bw() +
  ggtitle("Skew") +
  scale_color_viridis_d(end = .8) +
  ylim(0, 1) +
  theme(legend.position = "none")

simpson_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_simpson_low, color = singletons, size = as.factor(nsites))) +
  geom_point() +
  theme_bw() +
  ggtitle("Simpson") +
  scale_color_viridis_d(end = .8)+
  ylim(0, 1) +
  theme(legend.position = "none")

>>>>

skew_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_skew_high, color = singletons, size = as.factor(nsites))) +
  geom_point() +
  theme_bw() +
  ggtitle("Skew") +
  scale_color_viridis_d(end = .8) +
  ylim(0, 1) +
  geom_hline(yintercept = .05, color = "red") +
  theme(legend.position = "none")

simpson_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_simpson_low, color = singletons, size = as.factor(nsites))) +
  geom_point() +
  theme_bw() +
  ggtitle("Simpson") +
  scale_color_viridis_d(end = .8)+
  ylim(0, 1) +
    geom_hline(yintercept = .05, color = "red") +

  theme(legend.position = "none")
